---
title: "Script for Downloading N.C. Campaign Finance Reports into R"
author: Ryan Thornburg
date: September 18, 2019
output:
  md_document:
    variant: markdown_github
---

For this, you need two packages from the tidyverse.

```{r}
library(readr)
library(dplyr)
```

You have to drill down quite a way from https://cf.ncsbe.gov/CFOrgLkup/ before you find the url you want, but once you do, just replace the URL on line 18 with the URL for the "Export data to .csv" that you need.




```{r}

url <- "https://cf.ncsbe.gov/CFOrgLkup/ExportDetailResults/?ReportID=168216&Type=REC&Title=Cooper%20for%20North%20Carolina%20-%202019%20Mid%20Year%20Semi-Annual"
```


read_csv() does not do a great job here guessing the correct col_types, so we have to define them explicitly.


```{r}
receipts <- read_csv(url, skip=1, col_types = 
cols(
  Date = col_date("%m/%d/%Y"),
  `Is Prior` = col_logical(),
  Name = col_character(),
  `Street 1` = col_character(),
  `Street 2` = col_character(),
  City = col_character(),
  State = col_character(),
  `Full Zip` = col_character(),
  `Country Name` = col_character(),
  `Outside US Postal Code` = col_character(),
  Profession = col_character(),
  `Employers Name` = col_character(),
  Purpose = col_character(),
  `Receipt Type Desc` = col_character(),
  `Account Abbr` = col_double(),
  `Form Of Payment Desc` = col_character(),
  Description = col_character(),
  Amount = col_double(),
  `Sum To Date` = col_double()))
        
head(receipts)

```

Finally, we should rename the columns to remove spaces and generally promote brevity.

```{r}
names(receipts) <- c("date","prior","donor","street1","street2","city","state","zip","country","postal","profession","employer","purpose","type","accont","payment_form","description","amount","sum_to_date")
```

 